---
title: "StructuralBioinformatics"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PDB Statistics


Download a CSV file from the PDB site (accessible from “Analyze” > “PDB Statistics” > “by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project and use it to answer the following questions:

    Q: What percentage of structures in the PDB are solved by X-Ray and Electron Microscopy.

    Q: What proportion of structures in the PDB are protein?

    Q: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?

```{r}
stats <- read.csv("Data Export Summary.csv", row.names = 1)
View(stats)
```


```{r}
round(sum(stats$Proteins) / sum(stats$Total) * 100, 2)

```
```{r}
ans<- round(stats$Total / sum(stats$Total)* 100, 2)
names(ans) <- rownames(stats)
ans
```
 Q: What proportion of structures in the PDB are protein? 
 Answer above on L.30
 
 Q: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?
##Using bio3d to analyze structure
Use bio3d from CRAN
Access from the library

```{r}
library(bio3d)

pdb<- read.pdb("1hsg")
pdb
```



```{r}
library(bio3d)
```
```{r}
aa <- get.seq("1ake_A")
aa
```

```{r}
b <- blast.pdb(aa)
```

Adenylate kinase structure

```{r}
hits <- NULL
hits$pdb.id <- c('1AKE_A','4X8M_A','6S36_A','6RZE_A','4X8H_A','3HPR_A','1E4V_A','5EJE_A','1E4Y_A','3X2S_A','6HAP_A','6HAM_A','4K46_A','4NP6_A','3GMT_A','4PZL_A')
```
Download and parse the structures
```{r}
# Download releated PDB files
files <- get.pdb(hits$pdb.id, path="pdbs", split=TRUE, gzip=TRUE)
```
```{r}
# Align releated PDBs
pdbs <- pdbaln(files, fit = TRUE, exefile="msa")
```
```{r}
# Vector containing PDB codes for figure axis
ids <- basename.pdb(pdbs$id)
```
```{r}
# Draw schematic alignment
```


```{r}
plot(pdbs, labels=ids)
```
```{r}
library(bio3d.view)
library(rgl)
view(pdbs)
rglwidget(elementId="tmp")
```
```{r}
library(bio3d.view)
```
```{r}
pc <- pca(pdbs)
plot(pc)
```

```{r}
# Calculate RMSD
rd <- rmsd(pdbs)

# Structure-based clustering
hc.rd <- hclust(dist(rd))
grps.rd <- cutree(hc.rd, k=3)

plot(pc, 1:2, col="grey50", bg=grps.rd, pch=21, cex=1)
```
```{r}
# Calculate RMSD
rd <- rmsd(pdbs)

# Structure-based clustering
hc.rd <- hclust(dist(rd))
grps.rd <- cutree(hc.rd, k=3)

plot(pc, 1:2, col="grey50", bg=grps.rd, pch=21, cex=1)
```


```{r}
# NMA of all structures
modes <- nma(pdbs)
```
```{r}
plot(modes, pdbs, col=grps.rd)
```





