---
title: "Class10RMD"
author: "LP"
date: "2/7/2020"
output: html_document
---
## Save cancer data
Input data 
```{r}
wisc.df <- read.csv("WisconsinCancer.csv")
head(wisc.df)
``` 

```{r}
wisc.data <- as.matrix(wisc.df[,3:32])
head(wisc.data)
```
Q. How many cancer vs benign?
```{r}
```


```{r}
table(wisc.df$diagnosis)
```
```{r}
sum(wisc.df$diagnosis =="M")
```


```{r}
colnames(wisc.df)
```

Use `grep()` fn to see this
```{r}
grep("_mean", colnames(wisc.df), value=TRUE)
```

adding TRUE specified matches
We can take the `length()` of this to find how many matches there are
```{r}
length( grep("_mean", colnames(wisc.df)))
```


##Enter Principal Component Analysis

First should check whether input data should be scaled.

Look at mean and sd to see if they are similar? Check the sd() and mean() of all our columns in `wisc,data`
```{r}
round(apply(wisc.data, 2, sd), 2)
```
```{r}
#Perform PCA
wisc.pr <- prcomp(wisc.data, scale = TRUE)
summary(wisc.pr)
```

biplot is useless here -- need to cook our own PCA plot. Need to access results withing the`wisc.pr` object

```{r}
attributes(wisc.pr)
```

We want the $x component to make our PCA/score plot!
```{r}
plot(wisc.pr$x[, 1], wisc.pr$x[, 2], col=wisc.df$diagnosis)
```


## Moving to Hierarchical clustering
```{r}

wisc.hclust <-hclust(dist(wisc.pr$x[, 1:3]), method = "ward.D2")
                     
plot(wisc.hclust)   
                     
```
Jump ahead to Combine methods -- ccan cluster in PC space, brings in ward.D2
        
```{r}
## Predicting Malignancy Of New samples
url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata=new)

```

```{r}
plot(wisc.pr$x[,1:2], col=wisc.df$diagnosis)
points(npc[,1], npc[,2], col="blue", pch=16, cex=3)
text(npc[,1], npc[,2], c(1,2), col="white")
```

  
